## Exercises 
1\. Compute conditional probabilities for being Male for the `heights` dataset.  Round the heights to the closest inch. Plot the estimated conditional probability $P(x) = \mbox{Pr}(\mbox{Male} | \mbox{height}=x)$ for each $x$.
```{r}
library(dslabs)


heights %>% 
    mutate(height = round(height)) %>%
    group_by(height) %>%
    summarize(p = mean(sex == "Male")) %>%
    qplot(height, p, data = .)

```

2\. In the plot we just made, we see high variability for low values of height. This is because we have few data points in these strata. This time use the `quantile` function for quantiles $0.1,0.2,\dots,0.9$ and the `cut` function to assure each group has the same number of points. Hint: for any numeric vector `x`, you can create groups based on quantiles like this:  
```{r, eval=FALSE} 
ps <- seq(0, 1, 0.1)
heights %>% 
  mutate(g = cut(height, quantile(height, ps), include.lowest = TRUE)) %>%
	group_by(g) %>%
	summarize(p = mean(sex == "Male"), height = mean(height)) %>%
	qplot(height, p, data =.)
```

3\. Generate data from a bivariate normal distribution using the __MASS__ package like this: 

```{r}
Sigma <- 9*matrix(c(1,0.5,0.5,1), 2, 2)
dat <- MASS::mvrnorm(n = 10000, c(69, 69), Sigma) %>%
	data.frame() %>% setNames(c("x", "y"))
```	
And make a quick plot using 
You can make a quick plot of the data using `plot(dat)`. Use an approach similar to the previous exercise to estimate the conditional expectations and make a plot. 
```{r, include=TRUE}
plot(dat)
```

 
