## Exercises 
1\. Load the `GaltonFamilies` data from the __HistData__. The children in each family are listed by gender and then by height. Create a dataset called `galton_heights` by picking a male and female at random.  

```{r}
library(tidyverse) 
library(HistData) 
data("GaltonFamilies") 
GaltonFamilies

galton_heights = GaltonFamilies |> 
  group_by(family,gender) |> 
  sample_n(1)

galton_heights
```


2\. Make a scatterplot for heights between mothers and daughters, mothers and sons, fathers and daughters, and fathers and sons.  

```{r}
galton_heights1 = galton_heights |> 
  mutate(children = case_when(gender == "female" ~ "duaghter", gender == "male" ~ "son")) |>
  select(father, mother, children, childHeight) |>
  pivot_longer(3:4,names_to = "parent", values_to = "parentHeight")
  


galton_heights1 |> 
  ggplot(aes(x = parentHeight, y = childHeight, color = parent)) +
  geom_point() + 
  facet_wrap(.~children)

```


3\. Compute the correlation in heights between mothers and daughters, mothers and sons, fathers and daughters, and fathers and sons. 

```{r}
galton_heights1 |> 
  group_by(parent, children) |> summarise(correlation = cor(parentHeight, childHeight))
```

