## Exercises 
1\. Load the `GaltonFamilies` data from the __HistData__. The children in each family are listed by gender and then by height. Create a dataset called `galton_heights` by picking a male and female at random from each family.
```{r}
library(HistData)
library(tidyverse)
galton_heights <- GaltonFamilies |> group_by(family, gender) |> sample_n(1)
galton_heights
```


2\. Make a scatterplot for heights between mothers and daughters, mothers and sons, fathers and daughters, and fathers and sons.  
```{r}
galton_heights |> ggplot(aes(x = mother, y = childHeight)) +
  geom_point() +
  facet_wrap(gender ~. )
```
```{r}
galton_heights |> ggplot(aes(x = father, y = childHeight)) +
  geom_point() +
  facet_wrap(gender ~. )
```

3\. Compute the correlation in heights between mothers and daughters, mothers and sons, fathers and daughters, and fathers and sons. 
```{r}
galton_heights |> group_by(gender) |> summarise(correlation = cor(mother, childHeight))
galton_heights |> group_by(gender) |> summarise(correlation = cor(father, childHeight))
```

 
