---
title: "intro_ml_SK"
author: "Soomin Kim"
date: "2022-11-20"
output: html_document
---
## Exercises 
1\. For each of the following, determine if the outcome is continuous or categorical: 
a. Digit reader *categorical*
b. Movie recommendations *continuous 0-5*
c. Spam filter *categorical no spam vs spam*
d. Hospitalizations *continuous number of hospitalizations*
e. Siri (speech recognition) *categorical sound waves into words*

2\. How many features are available to us for prediction in the digits dataset? 
```{r}
library(dslabs) 
mnist <- read_mnist() 
str(mnist)
```

*784 features* (28x28 = 784 pixels) in the textbook


3\. In the digit reader example, the outcomes are stored here: 
```{r, eval=FALSE} 
library(dslabs) 
mnist <- read_mnist() 
y <- mnist$train$labels 
``` 
Do the following operations have a practical meaning? 
```{r, eval=FALSE} 
y[5] + y[6] 
y[5] > y[6] 
``` 
Pick the best answer: 
a. Yes, because $9 + 2 = 11$ and $9 > 2$. 
b. No, because `y` is not a numeric vector. 
c. No, because 11 is not a digit. It's two digits. 
*d. No, because these are labels representing a category not a number. A `9` represents a class not the number 9.* 

 
