## Exercises 
1\. Load the `GaltonFamilies` data from the __HistData__. The children in each family are listed by gender and then by height. Create a dataset called `galton_heights` by picking a male and female at random.  

```{r}
library(tidyverse)
library(HistData)

df <- GaltonFamilies

galton_heights <- sample_n(df, size=1000, replace = TRUE) |>
   summarize(gender)

galton_heights

```


```{r}

mean(galton_heights$gender == "male")
```

2\. Make a scatterplot for heights between mothers and daughters, mothers and sons, fathers and daughters, and fathers and sons.  

```{r}
galton_heights <- GaltonFamilies |>
  filter(gender == "female") |>
  group_by(family) |>
  sample_n(1) |>
  ungroup() |>
  select(mother, childHeight) |>
  rename(daughter = childHeight)

galton_heights |> 
  ggplot(aes(mother, daughter)) + 
  geom_point(alpha = 0.5) 

cor(galton_heights$mother, galton_heights$daughter)
```

```{r}
galton_heights <- GaltonFamilies |>
  filter(gender == "female") |>
  group_by(family) |>
  sample_n(1) |>
  ungroup() |>
  select(father, childHeight) |>
  rename(daughter = childHeight)

galton_heights |> 
  ggplot(aes(father, daughter)) + 
  geom_point(alpha = 0.5) 

cor(galton_heights$father, galton_heights$daughter)
```
```{r}
galton_heights <- GaltonFamilies |>
  filter(gender == "male") |>
  group_by(family) |>
  sample_n(1) |>
  ungroup() |>
  select(mother, childHeight) |>
  rename(son = childHeight)

galton_heights |> 
  ggplot(aes(mother, son)) + 
  geom_point(alpha = 0.5) 

cor(galton_heights$mother, galton_heights$son)
```

3\. Compute the correlation in heights between mothers and daughters, mothers and sons, fathers and daughters, and fathers and sons. 
```{r}
# it is in the prior chunk
```

 
