---
output: html_document
editor_options: 
  chunk_output_type: console
---
## Exercises 
1\. Load the `GaltonFamilies` data from the __HistData__. The children in each family are listed by gender and then by height. Create a dataset called `galton_heights` by picking a male and female at random.  

**ANSWER:**
```{r}
library(tidyverse)
library(HistData)
data("GaltonFamilies")

galton_heights <- GaltonFamilies |>
  group_by(family, gender) |>
  sample_n(1)
galton_heights
```


2\. Make a scatterplot for heights between mothers and daughters, mothers and sons, fathers and daughters, and fathers and sons.  

**ANSWER:**
```{r}
# mothers and children
galton_heights |> ggplot(aes(mother, childHeight, color = gender)) + 
  geom_point(alpha = 0.5) +
  labs(x= "mother height", y = "children height", color = "Child's gender")

# fathers and children
galton_heights |> ggplot(aes(father, childHeight, color = gender)) + 
  geom_point(alpha = 0.5) +
  labs(x= "father height", y = "children height", color = "Child's gender")
```

3\. Compute the correlation in heights between mothers and daughters, mothers and sons, fathers and daughters, and fathers and sons. 

**ANSWER:**
```{r}
galton_heights |> 
  group_by(gender) |>
  summarize(r_mother = cor(mother, childHeight), r_father = cor(father, childHeight))
```
