---
output: html_document
editor_options: 
  chunk_output_type: console
---
## Exercises 
1\. For each of the following, determine if the outcome is continuous or categorical: 

a. Digit reader **CATEOGORICAL**
b. Movie recommendations  **CONTINUOUS**
c. Spam filter **CATEGORICAL**
d. Hospitalizations **CONTINUOUS**
e. Siri (speech recognition) **CATEGORICAL**

2\. How many features are available to us for prediction in the digits dataset? 

**ANSWER: 28x28 = 784 features**

3\. In the digit reader example, the outcomes are stored here: 
```{r, eval=FALSE} 
library(dslabs) 
mnist <- read_mnist() 
y <- mnist$train$labels 
``` 
Do the following operations have a practical meaning? 
```{r, eval=FALSE} 
y[5] + y[6] 
y[5] > y[6] 
``` 
Pick the best answer: 

a. Yes, because $9 + 2 = 11$ and $9 > 2$.

b. No, because `y` is not a numeric vector. 
c. No, because 11 is not a digit. It's two digits. 
d. No, because these are labels representing a category not a number. A `9` represents a class not the number 9. 

**ANSWER: D**
