## Exercises 
1\. Load the `GaltonFamilies` data from the __HistData__. The children in each family are listed by gender and then by height. Create a dataset called `galton_heights` by picking a male and female at random.  

```{r}
library(tidyverse)
library(HistData)
df <- GaltonFamilies
galton_heights <- sample_n(df, size=1000, replace = TRUE) |>
   summarize(gender)
galton_heights
```

```{r}
set.seed(1883)

galton_heights <- GaltonFamilies |>
  group_by(family) |>
  sample_n(1) |>
  ungroup() |>
  select(father, childHeight) 
```

2\. Make a scatterplot for heights between mothers and daughters, mothers and sons, fathers and daughters, and fathers and sons.
```{r}
galton_q2a <- GaltonFamilies |>
  filter(gender == "female") 

 plot(galton_q2a$mother, galton_q2a$childHeight, main = "heights between mothers and daughters",
     xlab = "moms", ylab = "girls",
     pch = 19, frame = FALSE)
abline(lm(mother ~ childHeight, data = galton_q2a), col = "blue")

galton_q2b <- GaltonFamilies |>
  filter(gender == "male") 

 plot(galton_q2b$mother, galton_q2b$childHeight, main = "heights between mothers and daughters",
     xlab = "moms", ylab = "boys",
     pch = 19, frame = FALSE)
abline(lm(mother ~ childHeight, data = galton_q2b), col = "blue")
```

3\. Compute the correlation in heights between mothers and daughters, mothers and sons, fathers and daughters, and fathers and sons. 

```{r}
cor(galton_q2a$mother, galton_q2a$childHeight)
cor(galton_q2b$mother, galton_q2b$childHeight)
```
