## Exercises 
1\. Earlier we used logistic regression to predict sex from height. Use kNN to do the same. Use the code described in this chapter to select the $F_1$ measure and plot it against $k$. Compare to the $F_1$ of about 0.6 we obtained with regression. 
```{r}
library(caret)
library(genefilter) 
library(tibble)
library(tidyverse)
library(dplyr)
library(stringr)
library(dslabs)

dfq1 <- as.data.frame(heights)
set.seed(2007)
test_index <- createDataPartition(dfq1$sex, times = 1, p = 0.5, list = FALSE)

test_set <- dfq1[test_index, ]
train_set <- dfq1[-test_index, ]

modelLookup("knn")
train_knn <- train(sex ~ height, method = "knn", data = dfq1, tuneGrid = data.frame(k = seq(9, 71, 2)))
ggplot(train_knn, highlight = TRUE)

```
```{r}
train_glm <- train(sex ~ ., method = "glm", data = dfq1)
train_knn <- train(sex ~ ., method = "knn", data = dfq1)

y_hat_glm <- predict(train_glm, dfq1$test, type = "raw")
y_hat_knn <- predict(train_knn, dfq1$test, type = "raw")

confusionMatrix(y_hat_glm, dfq1$test$sex)$overall[["Accuracy"]]

confusionMatrix(y_hat_knn, dfq1$test$sex)$overall[["Accuracy"]]
```

2\. Load the following dataset: 
```{r, eval=FALSE} 
library(caret)
library(tibble)
library(tidyverse)
library(dplyr)
library(stringr)
library(dslabs)
data("tissue_gene_expression") 
df <- as.data.frame(tissue_gene_expression)


dat.2 <- as.data.frame(tissue_gene_expression)
dat.2 <- tibble::rownames_to_column(dat.2, "VALUE")

```

```{r}
df1 <- str_replace_all(dat.2$VALUE, "[:digit:]", "")
df1 <- gsub("\\_|\\]", "", df1)
```

```{r}
dat.2$VALUE <- df1
```

This dataset includes a matrix `x`:  
```{r, eval=FALSE} 
dim(tissue_gene_expression$x) 
``` 
with the gene expression measured on 500 genes for 189 biological samples representing seven different tissues. The tissue type is stored in `y`: 
```{r, eval=FALSE} 
table(tissue_gene_expression$y) 
``` 
Split the data in training and test sets, then use kNN to predict tissue type and see what accuracy you obtain. Try it for  $k = 1, 3, \dots, 11$. 

```{r}
set.seed(2000)
test_index <- createDataPartition(dat.2$VALUE, times = 1, p = 0.5, list = FALSE)

test_set <- dat.2[test_index, ]
train_set <- dat.2[-test_index, ]
```

Training and train control
```{r}

set.seed(4020)
ctrl <- trainControl(method="repeatedcv",repeats = 3) #,classProbs=TRUE,summaryFunction = twoClassSummary)
knnFit <- train(VALUE ~ ., data = train_set, method = "knn", trControl = ctrl, preProcess = c("center","scale"), tuneLength = 20)

#Output of kNN fit
knnFit
```
```{r}
plot(knnFit)

```

```{r}
knnPredict <- predict(knnFit,newdata = test_set )
#Get the confusion matrix to see accuracy value and other parameter values
confusionMatrix(knnPredict, as.factor(test_set$VALUE))

plot(knnFit, print.thres = 0.5, type="S")
```
 
