---
title: "knn_SK"
author: "Soomin Kim"
date: "2022-11-20"
output: html_document
---

## Exercises 
1\. Earlier we used logistic regression to predict sex from height. Use kNN to do the same. Use the code described in this chapter to select the $F_1$ measure and plot it against $k$. Compare to the $F_1$ of about 0.6 we obtained with regression.

```{r}

```


2\. Load the following dataset: 
```{r, eval=FALSE} 
library(dslabs)
data("tissue_gene_expression") 
``` 
This dataset includes a matrix `x`:  
```{r, eval=FALSE} 
dim(tissue_gene_expression$x) 
``` 
with the gene expression measured on 500 genes for 189 biological samples representing seven different tissues. The tissue type is stored in `y`: 
```{r, eval=FALSE} 
table(tissue_gene_expression$y) 
``` 
Split the data in training and test sets, then use kNN to predict tissue type and see what accuracy you obtain. Try it for  $k = 1, 3, \dots, 11$. 

```{r}
library(caret)
set.seed(1)
train_idx <- sample(c(1:189), size = round(0.8*189))#arbitrary 80% train used often
test_idx <- c(1:189)[-train_idx]
for (k in seq(1,11,2)) {
  fit <- knn3(tissue_gene_expression$x[train_idx,],
              tissue_gene_expression$y[train_idx],
              k=k)
  y_hat <- predict(fit,
                   tissue_gene_expression$x[test_idx,],
                   type = "class")
  print(paste0("k=",k))
  print(mean(tissue_gene_expression$y[test_idx]==y_hat))
}
```

