---
title: "reshaping_data_SK"
author: "Soomin Kim"
date: "2022-11-20"
output: html_document
---

## Exercises 

1\. Run the following command to define the `co2_wide` object: 
```{r, eval=FALSE} 
co2_wide <- data.frame(matrix(co2, ncol = 12, byrow = TRUE)) |>  
  setNames(1:12) |> 
  mutate(year = as.character(1959:1997)) 

co2_wide |> head()
``` 
Use the `pivot_longer` function to wrangle this into a tidy dataset. Call the column with the CO2 measurements `co2` and call the month column `month`. Call the resulting object `co2_tidy`. 

```{r}
co2_tidy <- co2_wide |> pivot_longer(1:12, names_to = "month", values_to = "co2") # !year
co2_tidy
```


2\. Plot CO2 versus month with a different curve for each year using this code: 
```{r, eval=FALSE} 
co2_tidy |> ggplot(aes(month, co2, color = year)) + geom_line() 
``` 
If the expected plot is not made, it is probably because `co2_tidy$month` is not numeric: 
```{r, eval=FALSE} 
class(co2_tidy$month) 
``` 
Rewrite your code to make sure the month column is numeric. Then make the plot.
```{r}
co2_tidy <- co2_tidy |> mutate(month = as.integer(month))

co2_tidy |> ggplot(aes(month, co2, color = year)) + geom_line() 
```


3\. What do we learn from this plot?  
a. CO2 measures increase monotonically from 1959 to 1997. 
*b. CO2 measures are higher in the summer and the yearly average increased from 1959 to 1997.* 
c. CO2 measures appear constant and random variability explains the differences. 
c. CO2 measures do not have a seasonal trend. 

4\. Now load the `admissions` data set, which contains admission information for men and women across six majors and keep only the admitted percentage column: 
```{r, eval=FALSE} 
library(dslabs)
data(admissions)
dat <- admissions |> select(-applicants) 
dat
``` 
If we think of an observation as a major, and that each observation has two variables (men admitted percentage and women admitted percentage) then this is not tidy. Use the `pivot_wider` function to wrangle into tidy shape: one row for each major. 

```{r}
dat2 <- dat |> pivot_wider(names_from = gender, values_from = admitted)
dat2
```


5\. Now we will try a more advanced wrangling challenge. We want to wrangle the admissions data so that for each major we have 4 observations: `admitted_men`, `admitted_women`, `applicants_men` and `applicants_women`.  The _trick_ we perform here is actually quite common: first use `pivot_longer` to generate an intermediate data frame and then `pivot_wider` to obtain the tidy data we want. We will go step by step in this and the next two exercises. 
Use the `pivot_longer` function to create a `tmp` data.frame with a column containing the type of observation `admitted` or `applicants`. Call the new columns `name` and `value`.  

```{r}
admissions
tmp <- admissions |> pivot_longer(cols = admitted:applicants, names_to = "name", values_to = "value")
tmp
```


6\. Now you have an object `tmp` with columns `major`,  `gender`, `name` and  `value`. Note that if you combine the `name` and `gender`, we get the column names we want: `admitted_men`, `admitted_women`, `applicants_men` and `applicants_women`. Use the function `unite` to create a new column called `column_name`. 

```{r}
tmp2 <- tmp |> unite(col = column_name, gender, name)
tmp2
```


7\. Now use the `pivot_wider` function to generate the tidy data with four variables for each major. 
```{r}
tmp3 <- tmp2 |> pivot_wider(names_from = column_name, values_from = value)
tmp3
```



8\. Now use the pipe to write a line of code that turns `admissions` to the table  produced in the previous exercise. 

```{r}
admissions |> pivot_longer(cols = admitted:applicants, names_to = "name", values_to = "value") |>
  unite(col = column_name, gender, name) |>
  pivot_wider(names_from = column_name,values_from = value)
```

 
