## Exercises 
Project Gutenberg is a digital archive of public domain books. The R package __gutenbergr__ facilitates the importation of these texts into R. 
You can install and load by typing: 
```{r, eval=FALSE} 
#install.packages("gutenbergr") 
devtools::install_github("ropensci/gutenbergr")
library(gutenbergr) 
``` 
You can see the books that are available like this: 
```{r, eval=FALSE} 
gutenberg_metadata 
``` 
1\. Use `str_detect` to find the ID of the novel _Pride and Prejudice_. 
```{r}
library(stringr)
gutenberg_metadata %>%
  filter(str_detect(title, "Pride and Prejudice"))  %>%
  summarise(gutenberg_id , title, author)
```
2\. We notice that there are several versions. The `gutenberg_works()` function filters this table to remove replicates and include only English language works. Read the help file and use this function to find the ID for _Pride and Prejudice_. 
```{r}
gutenberg_works() %>%
  filter(str_detect(title, "Pride and Prejudice"))  %>%
  summarise(gutenberg_id , title, author)
```
3\. Use the `gutenberg_download` function to download the text for Pride and Prejudice. Save it to an object called `book`. 
```{r}
book <- gutenberg_download(gutenberg_id = 1342)
```
4\. Use the __tidytext__ package to create a tidy table with all the words in the text. Save the table in an object called `words`
```{r}
library(tidytext)
words <-book %>% 
  unnest_tokens(word, text)
words
```
5\. We will later make a plot of sentiment versus location in the book. For this, it will be useful to add a column with the word number to the table.
```{r}
words %>% mutate(word_number = row_number())
```
6\. Remove the stop words and numbers from the `words` object. Hint: use the `anti_join`.  
```{r}
words <- anti_join(words,stop_words, by="word") %>% 
  filter(!word %in% c(1:100)) %>%
  arrange(word)
words
```
7\. Now use the `AFINN` lexicon to assign a sentiment value to each word. 
```{r}

library(textdata)
#get_sentiments("afinn")

afinn <- sentiments %>% filter(lexicon == "AFINN") %>% select(word, score)
book_score <- inner_join(book_words,afinn,by="word") 
```
8\. Make a plot of sentiment score versus location in the book and add a smoother.
```{r}
book_score %>% ggplot(aes(word_number,score)) + geom_point()
```
9\. Assume there are 300 words per page. Convert the locations to pages and then compute the average sentiment in each page. Plot that average score by page. Add a smoother that appears to go through data. 
```{r}
book_score %>% ggplot(aes(word_number,score)) + geom_smooth()

book_page <- book_score %>% mutate(page_number = round(word_number/300))
book_page %>% ggplot(aes(page_number,score)) + geom_smooth()
## `geom_smooth()` using method = 'gam' and formula 'y ~ s(x, bs = "cs")'

```

 
